True versus apparent shapes of bow shocks

### 2018-01-17 papers/Papers1234/sec-intro.tex
Partially address first point of referee - rad curvature
Add new appendixes to address referee points

The stagnation radius \(R_0\) describes the linear scale of the bow
shock, but in order to characterize its shape more parameters are
required.  To efficiently capture the diversity of bow shapes, we
propose the parameters shown in Figure~\ref{fig:characteristic-radii}.
The perpendicular radius \(R_{90}\) is the value of \(R(\theta)\) at
\(\theta = 90^\circ\), whereas \(R_{\C}\) is the radius of curvature of the bow at
the apex (\(\theta = 0\)), which in cylindrical symmetry simplifies to
\begin{equation}
  \label{eq:radius-curvature}
  R_{\C} 
  % = R_0 \Biggl[ 1
  % - \frac{1} {R_0} \left.\frac{d^2\! R} {d\,\theta^2}\right|_{\theta = 0} \Biggr]^{-1}
  = \frac{R_0^2}{R_0 - R_{\theta\theta,0}} \ , 
\end{equation}
where \(R_{\theta\theta,0}\) is \(d^2 \!R / d\theta^2\) evaluated at \(\theta = 0\).

>>>>

The stagnation radius \(R_0\) describes the linear scale of the bow
shock, but in order to characterize its shape more parameters are
required.  To efficiently capture the diversity of bow shapes, we
propose the parameters shown in Figure~\ref{fig:characteristic-radii}.
The perpendicular radius \(R_{90}\) is the value of \(R(\theta)\) at
\(\theta = 90^\circ\), whereas \(R_{\C}\) is the radius of curvature of the bow
at the apex (\(\theta = 0\)).  For a cylindrically symmetric bow, we show
in Appendix~\ref{sec:radius-curvature} that this is given by
\begin{equation}
  \label{eq:radius-curvature}
  R_{\C} 
  = \frac{R_0^2}{R_0 - R_{\theta\theta,0}} \ , 
\end{equation}
where \(R_{\theta\theta,0}\) is \(d^2 \!R / d\theta^2\) evaluated at \(\theta = 0\).

### 2018-01-17 papers/Papers1234/sec-projection.tex
Add new appendixes to address referee points

\newenvironment{Vector}{\left(\begin{array}{c}}{\end{array}\right)}
\newcommand\uvec[1]{\bm{\hat{#1}}}
\newcommand\T{_{\mathrm{\scriptscriptstyle T}}}

@@

Consider body-frame cartesian coordinates $(x,y,z)$, where \(x\) is
the symmetry axis, and spherical polar coordinates
\((R, \theta, \phi)\), where \(\theta\) is the polar angle and
\(\phi\) the azimuthal angle.  Since the surface is cylindrically
symmetric, it is can be specified as $R = R(\theta)$, so that
cartesian coordinates on the surface are:
\begin{equation}
  \begin{Vector}
    x \\ y \\ z
  \end{Vector} 
  = R(\theta)
  \begin{Vector}
    \cos\theta \\
    \sin\theta\cos\phi \\
    \sin\theta\sin\phi
  \end{Vector}.
  \label{eq:body-frame}
\end{equation} 
Suppose that the viewing direction makes an angle \(i\) with the
\(z\)~axis, so that we can define observer-frame coordinates
\((x', y', z')\), which are found by rotating the body-frame
coordinates about the \(y\)~axis:
\begin{equation}
  \begin{Vector}
    x' \\ y' \\ z'
  \end{Vector}
  = 
  \begin{Vector}
    x\cos i - z\sin i\\
    y \\
    z\cos i + x\sin i
  \end{Vector}.
  \label{eq:Trans}
\end{equation} 
The relationship between the two frames is illustrated in
Figure~\ref{fig:projection-pos}.  All quantities in the observer's
frame are denoted by attaching a prime to the equivalent quantity in
the body frame.  The celestial coordinates on the ``plane of the sky''
are given by \((x', y')\) with \(x'\) being the projected symmetry
axis of the surface, while the line of sight lies along \(-z'\).  The
inclination angle \(i\) is defined so that \(i = \ang{0}\) when the
surface is viewed perpendicular to its axis (\textit{side on}) and
\(i = \ang{90}\) when it is viewed along its axis (\textit{end on}).

@@

\subsection{Unit vectors normal and tangential to the surface}
\label{sec:unit-vectors-normal}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-unit-vectors}
  \caption{Unit vectors in the body frame that are normal and
    tangential to the surface \(R(\theta)\) in a plane of constant
    azimuth, \(\phi\).}
  \label{fig:unitvec}
\end{figure}
We define unit vectors \(\uvec{n}, \uvec{t}\), such that \(\uvec{n}\) is normal to the surface, while \(\uvec{t}\) is tangent to the surface in a plane of constant \(\phi\). For \(\phi = 0\) the surface lies in the \(xy\) plane and it is straightforward to show (Fig.~\ref{fig:unitvec}) that in this case the unit vectors are given by 
\begin{equation}
  \label{eq:uvec-phi0}
  \uvec{t}_0 =
  \begin{Vector}
    -\cos\alpha \\ \sin\alpha \\ 0
  \end{Vector}
  \quad \mathrm{and} \quad
  \uvec{n}_0 =
  \begin{Vector}
    \sin\alpha \\ \cos\alpha \\ 0
  \end{Vector}, 
\end{equation}
where \(\alpha\) is the \textit{slope angle}, given by
\begin{equation}
  \label{eq:alpha}
  \tan\alpha = -\left.\frac{dy}{dx}\right\vert_{R(\theta)} 
  = \frac{1 + \omega \tan\theta}{\tan\theta - \omega}
\end{equation}
and \(\omega\) is a dimensionless \textit{local growth factor}:
\begin{equation}
  \label{eq:omega}
  \omega(\theta) = \frac{1}{R} \frac{dR}{d\theta} . 
\end{equation}
For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis, and then
converting to the observer frame by use of equation~(\ref{eq:Trans})
to give
\begin{gather}
  \label{eq:nprime}
  \begin{split}
    \uvec{n}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
    & \times 
      \begin{Vector}
        (\cos\theta+\omega\sin\theta)\cos i 
        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
        (\sin\theta-\omega\cos\theta)\cos\phi \\
        (\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector}\\
  \end{split}\\
  \label{eq:tprime}
  \begin{split}
    \uvec{t}' = & \frac{1}{(1+\omega^2)^{1/2}} \\
    & \times 
      \begin{Vector}
        -(\sin\theta-\omega\cos\theta)\cos i
        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
        (\cos\theta+\omega\sin\theta)\cos\phi \\
        -(\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector}
  \end{split}
  \end{gather}
\subsection{Tangent line}
\label{sec:tangent-line}

>>>>

@@

Consider body-frame cartesian coordinates $(x,y,z)$, where \(x\) is
the symmetry axis, and spherical polar coordinates
\((R, \theta, \phi)\), where \(\theta\) is the polar angle and
\(\phi\) the azimuthal angle.  Since the surface is cylindrically
symmetric, it is can be specified as $R = R(\theta)$, so that
cartesian coordinates on the surface are:
\begin{equation}
  \bm{R} \equiv
  \begin{Vector}
    x \\ y \\ z
  \end{Vector} 
  = 
  \begin{Vector}
    R(\theta)\, \cos\theta \\
    R(\theta)\, \sin\theta\cos\phi \\
    R(\theta)\, \sin\theta\sin\phi
  \end{Vector}.
  \label{eq:body-frame}
\end{equation} 
Suppose that the viewing direction makes an angle \(i\) with the
\(z\)~axis, so that we can define observer-frame coordinates
\((x', y', z')\), which are found by rotating the body-frame
coordinates about the \(y\)~axis:
\begin{equation}
  \bm{R}' \equiv
  \begin{Vector}
    x' \\ y' \\ z'
  \end{Vector}
  = \mathbfss{A}_y(i)\, \bm{R}
  =
  \begin{Vector}
    x\cos i - z\sin i\\
    y \\
    z\cos i + x\sin i
  \end{Vector} \ ,
  \label{eq:Trans}
\end{equation}
where the rotation matrix \(\mathbfss{A}_y(i)\) is given in Appendix~\ref{sec:plane-sky-projection}. 
The relationship between the two frames is illustrated in
Figure~\ref{fig:projection-pos}.  All quantities in the observer's
frame are denoted by attaching a prime to the equivalent quantity in
the body frame.  The celestial coordinates on the ``plane of the sky''
are given by \((x', y')\) with \(x'\) being the projected symmetry
axis of the surface, while the line of sight lies along \(-z'\).  The
inclination angle \(i\) is defined so that \(i = \ang{0}\) when the
surface is viewed perpendicular to its axis (\textit{side on}) and
\(i = \ang{90}\) when it is viewed along its axis (\textit{end on}).

@@

\subsection{Unit vectors normal and tangential to the surface}
\label{sec:unit-vectors-normal}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/bowshock-unit-vectors}
  \caption{Unit vectors in the body frame that are normal and
    tangential to the surface \(R(\theta)\) in a plane of constant
    azimuth, \(\phi\).}
  \label{fig:unitvec}
\end{figure}
We define unit vectors \(\uvec{n}, \uvec{t}\), such that \(\uvec{n}\) is normal to the surface, while \(\uvec{t}\) is tangent to the surface in a plane of constant \(\phi\). For \(\phi = 0\) the surface lies in the \(xy\) plane and it is straightforward to show (Fig.~\ref{fig:unitvec}) that in this case the unit vectors are given by 
\begin{equation}
  \label{eq:uvec-phi0}
  \uvec{t}_0 =
  \begin{Vector}
    -\cos\alpha \\ \sin\alpha \\ 0
  \end{Vector}
  \quad \mathrm{and} \quad
  \uvec{n}_0 =
  \begin{Vector}
    \sin\alpha \\ \cos\alpha \\ 0
  \end{Vector}, 
\end{equation}
where \(\alpha\) is the \textit{slope angle}, given by
\begin{equation}
  \label{eq:alpha}
  \tan\alpha = -\left.\frac{dy}{dx}\right\vert_{R(\theta)} 
  = \frac{1 + \omega \tan\theta}{\tan\theta - \omega}
\end{equation}
and \(\omega\) is a dimensionless \textit{local growth factor}:
\begin{equation}
  \label{eq:omega}
  \omega(\theta) = \frac{1}{R} \frac{dR}{d\theta} . 
\end{equation}
For general \(\phi\), we find \(\uvec{n}\) and \(\uvec{t}\) by rotating
equations~(\ref{eq:uvec-phi0}) around the \(x\)-axis with the matrix
\(\mathbfss{A}_x(\phi)\)(see Appendix~\ref{sec:plane-sky-projection}) and
then converting to the observer frame by use of
equation~(\ref{eq:Trans}) to give
\begin{gather}
  \label{eq:nprime}
  \begin{aligned}
    \uvec{n}' &= \mathbfss{A}_y(i)\, \uvec{n}
    = \mathbfss{A}_y(i)\, \mathbfss{A}_x(\phi)\, \uvec{n}_0 \\
    & =
    \begin{aligned}[t]
      & \frac{1}{(1+\omega^2)^{1/2}} \\
      & \times 
      \begin{Vector}
        (\cos\theta+\omega\sin\theta)\cos i 
        - (\sin\theta-\omega\cos\theta) \sin i \sin\phi\\
        (\sin\theta-\omega\cos\theta)\cos\phi \\
        (\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector}
    \end{aligned}
  \end{aligned}\\
  \label{eq:tprime}
  \begin{aligned}
    \uvec{t}' &= \mathbfss{A}_y(i)\, \uvec{t}
    = \mathbfss{A}_y(i)\, \mathbfss{A}_x(\phi)\, \uvec{t}_0 \\
    & =
    \begin{aligned}[t]
      & \frac{1}{(1+\omega^2)^{1/2}} \\
      & \times 
      \begin{Vector}
        -(\sin\theta-\omega\cos\theta)\cos i
        - (\cos\theta+\omega\sin\theta)\sin\phi\sin i \\
        (\cos\theta+\omega\sin\theta)\cos\phi \\
        -(\cos\theta+\omega\sin\theta)\sin i 
        + (\sin\theta-\omega\cos\theta)\sin\phi\cos i
      \end{Vector} \ .
    \end{aligned}
  \end{aligned}
\end{gather}
\subsection{Tangent line}
\label{sec:tangent-line}
